### 2023-03-06 about/vita.tex
Small updates
New books and updated resume

\begingroup\frenchspacing
\papercount=5
\pubbegin P
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
To appear in {\sl Combinatorics, Probability and Computing}, 20~pp. [arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\parindent=10pt
\thing (with Jonah Saks)
Alternating-sum statistics for certain sets of integers. {\sl arXiv:2206.12535} (2022), 12~pp.
\endgroup
\endgroup%end the frenchspacing

@@

\starleftright{\bf Software developer}{\bf January 2023 -- present}
\leftright{\bf Levven}{\sl Edmonton, AB, Canada}
\smallskip
Develop firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Code primarily in \CEE\ and Python.
\medbreak

>>>>

\begingroup\frenchspacing
\papercount=5
\pubbegin P
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\parindent=10pt
\thing An uncertainty principle for M\"obius inversion on posets. {\sl arXiv:2302.02466} (2023), 7~pp.
\smallskip
\thing (with Jonah Saks)
On the homology of several number-theoretic set families. {\sl arXiv:2206.12535} (2022), 16~pp.
\endgroup
\endgroup%end the frenchspacing

@@

\starleftright{\bf Software developer}{\bf January 2023 -- present}
\leftright{\bf Levven}{\sl Edmonton, AB, Canada}
\smallskip
Develop firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Code primarily in \CEE\ and Python. Contributed to the open-source
Mongoose OS codebase.
\medbreak
